\documentclass[a4paper,10pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip} % For better spacing between paragraphs
\usepackage{multicol} % For multi-column layout

% Set spacing for sections
\titlespacing{\section}{0pt}{*1.5}{*0.8}

% Set hyperlink options
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdfborder={0 0 0}
}

% Custom section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Nalin Kumar Gupta}} \\
    333/2 Sector 37A, Chandigarh \\
    +91 6280704506 \\
    \href{mailto:nalinkrgupta@gmail.com}{nalinkrgupta@gmail.com} \\
    \href{https://www.linkedin.com/in/nalin-kumar-gupta-450a98270/}{LinkedIn: nalin-kumar-gupta} | 
    \href{https://github.com/Nalin-kumar-gupta}{GitHub: Nalin-kumar-gupta} \\
\end{center}

\vspace{-1mm}

\section*{Professional Experience}

\textbf{Summit Technology Group India} \hfill Panchkula, India \\
\textit{Software Engineer Intern} \hfill Dec 2023 – Jul 2024 \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Enhanced disbursement and reversal process efficiency, reducing transaction times by 20\%.
    \item Integrated multiple banks into the company's API ecosystem, improving financial transactions.
    \item Identified and resolved critical production issues, increasing system uptime and reliability.
    \item Managed end-to-end responsibility for a bank's SDK development.
\end{itemize}

\vspace{-1mm}
\textbf{Trantor Software Pvt. Ltd.} \hfill Chandigarh, India \\
\textit{Python Backend Intern} \hfill Jun 2023 – Jul 2023 \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Developed proof of concepts for internal tools to improve operational efficiency.
    \item Debugged critical backend issues, improving overall system performance.
\end{itemize}

\vspace{-1mm}

\section*{Projects}

\textbf{Smart Walmart Packager} \hfill \href{https://nalin-kumar-gupta.github.io/swp-demo/index.html}{GitHub Link} \\
Awarded first place at Walmart’s Converge event \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Developed a SaaS application to optimize truck loading processes at warehouses.
    \item Generated 3D AR models to visualize space-optimized and axle-weight balanced packing for trucks.
    \item Technologies: Docker, Django, Three.js, React, Redis, PostgreSQL, Celery.
\end{itemize}

\vspace{-1mm}
\textbf{Malicious File Detection and Dynamic Analysis} \hfill \href{https://nalin-kumar-gupta.github.io/amd-demo/}{GitHub Link} \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Developed a real-time framework to analyze the behavior of malicious files using virtual machines.
    \item Utilized machine learning models to predict malicious activity based on behavioral analysis.
    \item Technologies: Cuckoo Sandbox, Docker, Decision Trees, Python.
\end{itemize}

\vspace{-1mm}
\textbf{Weed Classification Using Deep Learning Models} \hfill \href{https://nalin-kumar-gupta.github.io/weed-classifi-demo/}{GitHub Link} \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Built a web application for image upload and weed classification using deep learning models.
    \item Implemented ResNet50 and VGG16 models to achieve accurate classification.
    \item Technologies: Django, React, ResNet50, VGG16.
\end{itemize}

\vspace{-1mm}
\textbf{Offline Mobile Loan Application} \hfill  \\
\vspace{-5mm}
\begin{itemize}[noitemsep]
    \item Developed a cross-platform mobile application for submitting loan applications offline.
    \item Technologies: Docker, Django, React, Firebase.
\end{itemize}

\vspace{-1mm}
\section*{Education}

\textbf{Punjab Engineering College, Chandigarh} \hfill Dec 2021 – Jun 2025 \\
\textit{Bachelor of Technology in Computer Science \& Engineering}

\vspace{-1mm}
\textbf{St. Stephens School, Chandigarh} \hfill 2009 – 2019 \\
\textit{ICSE Board}

\vspace{-1mm}
\section*{Key Achievements}

\textbf{Walmart Sparkathon Winner} \hfill September 2024 \\
Secured first place in Walmart’s all-India Sparkathon, competing against 13,700+ participants.

\vspace{-1mm}
\textbf{STGI Annual Interns Day Winner} \hfill May 2024 \\
Awarded as one of the best presenter among 75 interns.

\vspace{-1mm}
\textbf{STGI Coding Hackathon Special Mention} \hfill October 2023 \\
Recognized for developing a real-time analytics tool during a 24-hour hackathon.

\vspace{-1mm}
\textbf{GATE Computer Science \& Engineering} \hfill Feb 2024 \\
Achieved an AIR under 1200 in the GATE examination.

\vspace{-1mm}
\textbf{KVPY Scholar} \hfill  January 2021 \\
Cleared the KVPY exam with an outstanding All-India rank.

\end{document}
